Title Goes Here

### 2020-01-30 paper/paper.tex
Started section on recovering standard match semantics
Basic 'abs' for pattern matching
More of 'abs' definition
More on 'construct' and 'Construct'

@@

@@

>>>>

\section{Recovering standard semantics for pattern matches}

\begin{lstlisting}
sumMatchAbs :: ERep s => SumMatch (ERepTy s) t -> s -> t
...

prodMatchAbs :: ERep s => ProdMatch s t -> s -> t
...

abs :: E t -> t
abs (CaseExp x f) = sumMatchAbs f (abs x)

abs (LeftExp x) = Left (abs x)
abs (RightExp y) = Right (abs y)
abs (PairExp x y) = (abs x, abs y)

abs (Repped x) = unrep x
...
\end{lstlisting}

@@

\ttt{construct} is designed to bring Haskell constructors into the EDSL world.

@@

The "helper constructor" \ttt{Construct} is part of the \ttt{E} type:

\begin{lstlisting}
data E t where
  ...
  Construct :: (a -> b) -> E (a -> b)
  ...
\end{lstlisting}
